\documentclass[paper=a4,fontsize=15pt]{scrartcl}

% packages
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor}
\usepackage{geometry}
\usepackage{mfirstuc}
\usepackage{anyfontsize}
\usepackage{soul}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{wrapfig}
\usepackage{sectsty}

\RedeclareSectionCommand[
  %runin=false,
  beforeskip=\baselineskip,
  afterskip=.5\baselineskip]{section}

\sectionfont{\fontsize{18}{10}\selectfont}


\pagestyle{empty}
\geometry{left=1.2cm, top=1.2cm, right=1.2cm, bottom=1.2cm, footskip=.5cm}

% set underscore \ul{} x pt below contents
\setul{2pt}{.4pt}

% set default font
\renewcommand{\familydefault}{\sfdefault}

% fat cdot
\makeatletter
\newcommand*\bigcdot{\mathpalette\bigcdot@{.5}}
\newcommand*\bigcdot@[2]{\mathbin{\vcenter{\hbox{\scalebox{#2}{$\m@th#1\bullet$}}}}}
\makeatother

% macros ------------------------------------------------------------------------------
% -------------------------------------------------------------------------------------

% helpers
\newcommand{\smallspace}{\vspace*{0.1em}}
\newcommand{\quarterspace}{\vspace*{0.25em}}
\newcommand{\halfspace}{\vspace*{0.5em}}

% header
\newcommand{\https}[1]{\href{https://#1}{\ul{#1}}}
\newcommand{\email}[1]{\href{mailto:#1}{\ul{#1}}}

\begin{document}

\begin{center}
  {\fontsize{35}{40}\selectfont Vasiliy Morkovkin \par}
  \halfspace
  \smallspace
  \smallspace

  {\normalsize
    \email{morkovkin.vv@phystech.edu}
    $\bigcdot$ \https{susliko.dev}
    $\bigcdot$ \https{github.com/susliko}
    \par}
\end{center}

\section*{Education}{}
\noindent \href{https://mipt.ru/english/}{\textbf{\ul{Moscow Institute of Physics and Technology}}}
{\hfill \footnotesize \textit{Sep 2016 - Jun 2020}} \par
\noindent Bachelor of Computer Science \par
\quarterspace
\footnotesize
\noindent 4.4 / 5.0 GPA

\noindent \href{https://mipt.ru/english/}{\textbf{\ul{Moscow Institute of Physics and Technology}}}
{\hfill \footnotesize \textit{Sep 2020 - Present}} \par
\noindent Master of Computer Science \par
\quarterspace
\footnotesize

\section*{Experience}{}
\normalsize
\noindent \href{https://www.tinkoff.ru}{\textbf{\ul{Tinkoff.ru}}}
$\vert$ \small Software Engineer \& Team Lead
{\hfill \footnotesize \textit{Since Feb 2018 (4 years)}}
\begin{itemize}[noitemsep,leftmargin=20pt,label=\raisebox{0.25ex}{\tiny$\bullet$},topsep=5pt]
  \small
  \item Developed services for travellers in functional-style Scala.
  \item Led a team, held architecture design interviews, mentored new employees.
  \item Designed libraries, APIs and abstractions, reducing the integration friction.
  \item Transited from monolith to microservice Kubernetes-based architecture with the growth of the codebase.
  \item Promoted the use of asynchronous message-broker based architectures.
  \item Adopted Bazel build system with a fine-grained caching mono-repository approach. This led to an increase in the level of code reuse and reduced build times in several times.
  \item Popularized functional programming as a highly-composable software engineering tool via talks and library development.
  \item Encouraged usage of TLA\textsuperscript{+} model-checking for system analysis.
\end{itemize}

\section*{Teaching and OSS}{}
\begin{itemize}[noitemsep,leftmargin=20pt,label=\raisebox{0.25ex}{\tiny$\bullet$},topsep=5pt]
  \item Co-author of a free introduction \href{https://stepik.org/course/16243}{\ul{course to Scala}} with 12k enrollments.
  \item \href{https://www.youtube.com/watch?v=8KxWi0xuDKs&t=15s}{\ul{Speaker}} at Scala Russia Conference. ``Rapid building of admin applications with Server-side Rendering in Scala''.
  \item Author of an open-source \href{https://github.com/susliko/lotos}{\ul{library}} for testing concurrent data-structures in Scala.
  \item Co-author of an open-source \href{https://github.com/susliko/tla.nvim}{\ul{Neovim plugin}} for TLA+ support.
  \item Contributor of the PlusCal \href{https://github.com/tlaplus-community/tree-sitter-tlaplus/}{\ul{tree-sitter grammar}}.
  \item Lecturer at Tinkoff Fintech Scala School.
\end{itemize}

\section*{Programming skills}{}
\begin{itemize}[noitemsep,leftmargin=20pt,label=\raisebox{0.25ex}{\tiny$\bullet$},topsep=5pt]
    \item \textit{Primary}: Scala, Java, TLA+.
    \item \textit{Pet-projects}: Rust, Lua, C/C++, Python.
    \item \textit{Scripting/Reading}: Haskell, Erlang, Go, JavaScript, Clojure, etc.
\end{itemize}

\section*{Technical interests}{}
\begin{itemize}[noitemsep,leftmargin=20pt,label=\raisebox{0.25ex}{\tiny$\bullet$},topsep=5pt]
    \item Distributed Fault-Tolerant Systems: Kafka, Cassandra, Spanner and Calvin-based databases.
    \item Developer tooling: IDE plugins, programming language grammars, etc.
\end{itemize}

\end{document}
